---
title: "Linear Model w/prediction"
author: "Nicole orizino"
date: "spring 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 



You can import the data directly from a link to its website.  Copy that link to the clipboard by right clicking on Raw Data and then copy link.


#                          SIMS~ARM

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```


```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```
  
  
 This is the scatter plot shows positive relations between ARM & SIMS. Equation of the line is SIMS= -4.1 + 0.05 * ARM. The adjusted R squared is 0.47. Residual Standard Error is 1.226, the residual standard Error is the standard deviation of the normal spread of errors on any point of the line. 
  
  
# Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

This shows the cor dtad of SIMS & ARM

# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```


This is showing that the residuals of the min, median and max is: -3.6467 -0.0285  3.0770, and the P value is greater than 0.00000000000000022 (very small). 

```{r}
newdata=data.frame(GRIP=94,ARM=88)
predict(model.1,newdata,interval="prediction")
```

This is showing the prediction of Model.1 and its equation SIMS=  -4.1 + 0.05 * ARM. Also a new cunk was added to predict the models.


# now add the model fit to our plot
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 



The equation of SIMS explained by ARM is
SIMS= -4.1 + 0.05 * ARM.

This graph shows the positive relations between SIMS & ARM.


#                     SIMS~GRIP







```{r}
basicGG <- ggplot(data,aes(y=SIMS,x=GRIP))
```
##Now add in scatterplot

```{r}
basicGG + geom_point()
```
  
 This is the scatter plot shows positive relations between GRIP & SIMS. Equation of the line is SIMS= -4.80 + 0.0455 * GRIP. The adjusted R squared is 0.405. Residual Standard Error is 1.295, the residual standard Error is the standard deviation of the normal spread of errors on any point of the line.  
  
  
  
# Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

This shows the cor data for SIMS~GRIP is 0.064.

# Inferential  (Build linear model)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
predict(model.2,newdata,interval="prediction")
```

This is showing that the prediction of Model.2 and its equation of SIMS, SIMS= -4.80 + 0.0455 * GRIP.
# now add the model fit to our plot
  
```{r}
basicGG + geom_point() + geom_smooth(method=lm)
``` 


The equation of SIMS explained by GRIP is
SIMS= -4.80 + 0.0455 * GRIP
This is the scatter plot shows positive relations between GRIP & SIMS.



#                   SIMS~ARMS+GRIP




```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```




# Inferential  (Build linear model)
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
predict(model.3,newdata,interval="prediction")
```


This is showing the prediction of model.3 and its equation. The equation of SIMS is -5.43 + 0.037 * ARM + 0.024 * GRIP  


```{r}
anova(model.1,model.3)
```
This is comparing all the models to see which is the best/ has less errors.
P-value= 0.00000499

# conclution
The P-value is very small (0.00000499) so we reject the Null Hypothesis. Conclusion is that Model.3 is the best model, the bigger the better.



